\chapter{Results and Future Scope}
\par
It is observed that the system performs all the functionalities as expected. The main aim behind this venture was to solve the issues related to the customer loyalty using the blockchain technology. The retailer can  successfully login and generate discount coupons, edit and digitally sign the coupons. Anyone can verify the credibility  of the coupons generated.
\section{Advantages and Limitations}
The proposed system features a lot of advantages over the existing system. It solves the problems of the existing system. The proposed system is way more secure than the existing system in many ways. Like any other system, this system also has its own advantages and limitations. The point is that its advantages override its limitations.
\subsection{Advantages}
\begin{itemize}
\item The system proposes an innovative blockchain based solution to customer loyalty problem 
\item The authentication data of the credential which gets published to blockchain is immutable, trustful and verifiable.
\item The new approach of verifying the coupons(scan the QR code) simplified the workflow to be more efficient.
\item The system can save the organization from the huge loss that can happen in long run.
\item The core data of the credential is secure and private even the blockchain technology crashes in the future.

\end{itemize}
\subsection{Limitations}
\begin{itemize}
\item Nowadays, the applications related to the blockchain technology are still in the experimental phase.
\item The blockchain technology is not widely accepted by the public since most of the people trust third-party organizations.
\item The retailer needs to use the private key to login to the system. However, the private key is a set of some irregular hexadecimal characters which is hard to remember.
\end{itemize}
\section{Future Extensions}
\par
The system can be generalized so that in future the online shopping websites can incorporate our system to scale their architecture. Also if a supply chain management system using the blockchain was added along, it will be more useful.
\par The combination of AI with our system can increase the overall profit of the retail chain as the retailer can use machine learning techniques to choose for which product the discount has to applied and what should be the discount for that particular product. So in future we are trying to scale our architecture into a fully fledged e-commerce company.

