\chapter{Introduction}
\par
The paper coupon market has been with us almost since shopping was 
first invented. Practically all retail outlets, big or small, have used coupons at least
once in their lives. The primary motivation is either to attract more customers by
offering them a discount or to enable them to pay in advance for gift vouchers that
are subsequently passed on to third parties. The major disadvantage of the paper
based coupon was its cost and difficulties in distribution of the coupons. Also the
accounting process becomes extremely time consuming. There are issues related
to study the market feedback. A very high proportion of paper coupons are never
returned. Paradoxically, a bigger problem is that no firm evidence can be identified
to help explain why some actually are returned! All these problems can be solved
by digitizing the coupon industry. But a major problem arises due to the arrival of
digital coupons. The coupons are getting manipulated by some individuals, which
causes a lot of loss to the merchants. So in many situations the loyalty of the
customer has to be cross validated by the retailers.
\par
With the normal encryption mechanism, up to a certain extent this problem
can be solved. But if the attacker was highly skilled with tremendous computation
power those techniques wont last long. We approach this problem with the disruptive
technology, the blockchain. The retailers can generate coupons for a particular
product and can share it with the universe using any social media. The coupons are
stored in an open source blockchain platform called Ethereum. With the underlying
security mechanism of the ethereum blockchain, our system was tamper-proof, as
till date nobody was able to break the blockchain network.
\par
Blockchain is a distributed ledger that was originally
proposed as the underlying technology for bitcoin and other cryptocurrencies, 
and has since been applied to non-monetary applications.
Blockchain is immutable as it is jointly managed by network participants
through a consensus mechanism, such as Proof-of-Work
(PoW), Proof-of-Stake (PoS), or Proof-of-ElapsedTime (PoET). 
Consensus delivers agreement among
the network participants, which are untrusted, on the
current state of the ledger. In effect, trust in the current
state is decentralised due to its coupling to the outcome
of distributed consensus among the participants.